AtmoSwing (v1.4): Analog Technique Model for Statistical weather forecastING

### 2015-11-03 AtmoSwing - Geoscientific Model Development/template.tex
Adding some content to the abstract.

AtmoSwing is an open source software that implement the analogue method in a very flexible way, so that different variants can be handled dynamically, by parameterization. It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the statistical relationship between the predictand and predictors.

The Optimizer integrates the most used technique, that is a semi-automatic sequential approach, as well as Monte-Carlo analyses, and especially a global optimization technique by means of Genetic algorithms.

%TODO: rewrite

@@

%TODO: rework

>>>>

AtmoSwing is an open source software that implement the analogue method in a very flexible way, so that different variants can be handled dynamically, by parameterization trough XML files. It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the statistical relationship between the predictand and predictors.

The Forecaster handles every required step internally, such as predictors downloading and parsing, grid interpolation, analogy sorting, without external scripts or file conversion. The processing of a forecast is extremely lightweight in terms of IT infrastructure; it can indeed run on almost any computer.

The Viewer displays the forecasts in an interactive GIS environment. It contains several layers of syntheses and details in order to provide a quick overview of the potential critical situations in the coming days, as well as the possibility for the user to go into the details of the forecasted predictand and criteria distributions. Several tips coming from the literature are provided in order to help interpreting the forecasts.

The Optimizer integrates the most used technique, that is a semi-automatic sequential approach, as well as Monte-Carlo analyses, and a global optimization technique by means of Genetic algorithms. It allows establishing the statistical relationship between predictors and predictands.

@@
